---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)

# NeighborhoodChangeTypology

[`NeighborhoodChangeTypology`](https://github.com/tiernanmartin/NeighborhoodChangeTypology) provides a framework for
understanding the different phases and types of neighborhood change that are occurring in communities throughout
King County, Washington.

## Installation

You can install [`NeighborhoodChangeTypology`](https://github.com/tiernanmartin/NeighborhoodChangeTypology) from
its Github [repository](https://github.com/tiernanmartin/NeighborhoodChangeTypology):

```{r, eval = FALSE}
devtools::install_github("tiernanmartin/NeighborhoodChangeTypology")
```

## Note

As of March 4, 2019, this package currently depends on an outdated version of the [`osfr`](https://centerforopenscience.github.io/osfr/) R package (v0.1). An update to [`NeighborhoodChangeTypology`](https://github.com/tiernanmartin/NeighborhoodChangeTypology) will change the [`osfr`](https://centerforopenscience.github.io/osfr/) -related code to the most recent version of the [`osfr`](https://centerforopenscience.github.io/osfr/) API.

This project is a work-in-progress. 
